Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Final version

\begin{abstract}
We investigate the notion of causality in modelling stationary time series. Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM). The CGPCM models the kernel of a Gaussian process nonparametrically and has an inductive bias towards causally-generated time series. We develop enhanced variational inference and learning schemes and demonstrate the CGPCM on synthetic and real-world signals.
\end{abstract}

>>>>

\begin{abstract}
This paper presents the Causal Gaussian Process Convolution Model (CGPCM), a doubly nonparametric model for causal, spectrally complex dynamical phenomena. The CGPCM is a generative model in which white noise is passed through a causal, nonparametric-window moving-average filter, which we show to be equivalent to a Gaussian process with a nonparametric kernel that is biased towards causally-generated signals. We develop enhanced variational inference and learning schemes for the causal and previous acausal variants of the GPCM \citet{Tobar:2015:Learning_Stationary} that significantly improve statistical accuracy. These modelling and inferential contributions are finally demonstrated on synthetic and real-world signals.
\end{abstract}
